\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
minor

\subsection{Consistency and Liveness}
\textbf{Lemma 2}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, and $t_1 \leq t_2$, then $g_p^1 \leq g_q^2$.
\todo{This is wrong\ldots}
What about: If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, and $t_1 \leq t_2$, then $g_p^1$ and $g_q^2$ are compatible.

>>>>

\subsection{Consistency and Liveness}
\textbf{Lemma 2}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, and $t_1 \leq t_2$, then $g_p^1 \leq g_q^2$.
\todo{This is wrong\ldots
What about: If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, and $t_1 \leq t_2$, then $g_p^1$ and $g_q^2$ are compatible.}
